stupid backoff

### 2019-11-25 al_stup.Rmd
stupid backoff function correction minor additions to server.R

getSQLFinalProbs = function(bigPre, unigs) {
    querry = paste("SELECT * FROM trigs WHERE ngram like '", 
                   bigPre, "_%' ORDER BY freq DESC", sep = "")
    my.dat = as.data.table(sqldf(querry))
    if(nrow(my.dat) < 1) {
        my.dat = getSQLBigProbs(bigPre, bigrs)
        if(nrow(my.dat) < 1) {
            my.dat = getUnigProbs(unigs)[, freq := freq * 0.4]
            return(my.dat)
        } else {
            my.dat = my.dat[, freq := freq * 0.16]
            return(my.dat)}
    } else {
        total_count = my.dat[, sum(freq)]
        my.dat = my.dat[ , freq := freq/total_count]
        return(my.dat)
    }

getSQLTrigProbs = function(bigPre, trigrams) {
    querry = paste("SELECT * FROM trigs WHERE ngram like '", 
                   bigPre, "_%' ORDER BY freq DESC", sep = "")
    my.dat = as.data.table(sqldf(querry))
    total_count = my.dat[, sum(freq)]
    my.dat = my.dat[ , freq := freq / total_count][1:50]
    return(my.dat)
}

getSQLBigProbs = function(bigPre, bigrams) {
    w_i_1 <- str_split(bigPre, "_")[[1]][2]
    querry = paste("SELECT * FROM bigrs WHERE ngram like '",
                   w_i_1, "_%' ORDER BY freq DESC", sep = "")
    my.dat = as.data.table(sqldf(querry))
    total_count = my.dat[, sum(freq)]
    my.dat = my.dat[, freq := freq/total_count][1:50]
    return(my.dat)
}

>>>>

#to get the second word of each row
getAdjNgram = function(my.ngram) {
    samp = strsplit(my.ngram[1,ngram], split = "_")
    if(length(samp[[1]]) == 3) {
        my.ngram$ngram = str_split_fixed(my.ngram$ngram, "_", 3)[, 3]
        return(my.ngram)
    } else if(length(samp[[1]]) == 2) {
        my.ngram$ngram = str_split_fixed(my.ngram$ngram, "_", 2)[, 2]
        return(my.ngram)
    } else return(my.ngram)
}

#first_words <- str_split_fixed(obsBoBigrams$ngram, "_", 2)[, 1]

getSQLFinalProbs = function(bigPre, unigs) {
    ID = integer()
    querry = paste("SELECT * FROM trigs WHERE ngram like '", 
                   bigPre, "_%' ORDER BY freq DESC", sep = "")
    my.dat = as.data.table(sqldf(querry))
    if(nrow(my.dat) < 1) {
        my.dat = getSQLBigProbs(bigPre, bigrs)
        if(nrow(my.dat) < 1) {
            my.dat = getUnigProbs(unigs)[, freq := freq * 0.16]
            return(my.dat)
        } else {
            my.dat = my.dat[, freq := freq * 0.4]
            return(my.dat)}
    } else {
        return(my.dat)
    }
}

getSQLTrigProbs = function(bigPre, trigrams) {
    querry = paste("SELECT * FROM trigs WHERE ngram like '", 
                   bigPre, "_%' ORDER BY freq DESC", sep = "")
    my.dat = as.data.table(sqldf(querry))
    w_i_1 <- str_split(bigPre, "_")[[1]][2]
    querry = paste("SELECT * FROM bigrs WHERE ngram like '",
                   w_i_1, "_%' ORDER BY freq DESC", sep = "")
    my.dat.bigs = as.data.table(sqldf(querry))
    total_count = my.dat.bigs[, sum(freq)]
    my.dat = my.dat[ , freq := freq / total_count]
    return(my.dat)
}

getSQLBigProbs = function(bigPre, bigrams) {
    w_i_1 <- str_split(bigPre, "_")[[1]][2]
    querry = paste("SELECT * FROM bigrs WHERE ngram like '",
                   w_i_1, "_%' ORDER BY freq DESC", sep = "")
    my.dat = as.data.table(sqldf(querry))
    querry = paste("SELECT * FROM unigsFull WHERE ngram like '",
                   w_i_1, "' ORDER BY freq DESC", sep = "")
    my.dat.unig = as.data.table(sqldf(querry))
    total_count = my.dat.unig[, sum(freq)]
    my.dat = my.dat[, freq := freq/total_count]
    return(my.dat)
}
